Approaching Optimal Duplicate Detection in a Sliding Window

### 2020-05-09 samplepaper.tex
Arxiv version from COCOON

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\input{preamble}
%\usepackage{times}
\usepackage[moderate]{savetrees}
\usepackage{multicol}

@@

@@

\begin{document}
%
\title{Approaching Optimal Duplicate Detection in a Sliding Window}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Rémi Géraud--Stewart\inst{1} \and
Marius Lombard-Platet\inst{1,2} \and
David Naccache\inst{1}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
Be-ys Research Lab, Clermont-Ferrand, France\\
\email{\{first\}.\{last\}@ens.fr}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.

@@

We also analyse the security of our filters in an adversarial setting. 
\keywords{TODO}
\end{abstract}
%
%
%
\input{article_content}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
\bibliography{bibli_short}
%\bibliography{qhtv2}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[]{article}
%
\input{preamble}
%\usepackage{times}
%\usepackage[moderate]{savetrees}
\usepackage{multicol}

@@

\usepackage{authblk}
% Keywords command
\providecommand{\keywords}[1]
{
	\small	
	\textbf{\textit{Keywords---}} #1
}
\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

@@

\begin{document}
%
\title{Approaching Optimal Duplicate Detection in a Sliding Window}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author[1]{Rémi Géraud--Stewart}
\author[1,2]{Marius Lombard-Platet}
\author[1]{David Naccache}
\affil[1]{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France}
\affil[2]{Be-ys Research Lab, Clermont-Ferrand, France}
\affil[ ]{\texttt{\{first\}.\{last\}@ens.fr}}
%
\date{}
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
%Be-ys Research Lab, Clermont-Ferrand, France\\
%\email{\{first\}.\{last\}@ens.fr}
%}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.

@@

We also analyse the security of our filters in an adversarial setting. 
\keywords{Duplicate detection, Streaming algorithms, Sliding window}
\end{abstract}
%
%
%
\input{article_content}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

 \bibliographystyle{splncs04}

%\bibliography{bibli_short}
\bibliography{qhtv2}
